Introduction

### 2024-01-10 scripts/Introduction.Rmd
playing with burning raster

(identify difficulties)
A primary challenge in effectively restoring Earths terrestrial ecosystems is the lack of available plant germplasm (@national2023assessment).
Given the scale of our restoration needs, in most scenarios, the only sustainable source of seed is from grow-outs of wild harvested seed in agricultural settings.
Enormous efforts are now underway to increase the number of species, the number of populations within these species, and the genetic diversity of these populations available for restoration @national2023assessment.
However, difficulties in both the wild harvest and increase of seed exist are limiting our ability to develop adequate amounts of germplams.  
Herein, we identify prospective methods to increase the 1) number of species, 2) populations, and 3) genetic diversity of collections and 4) increase the success of agriculturally produced seed lots using Species Distribution Models and subsequent analysis of them intended to pair them more aptly with species biology and ecology.

@@

>>>>

A primary challenge in effectively restoring Earths terrestrial ecosystems is the lack of available plant germplasm (@national2023assessment, @merritt2011restoration).
Given the scale of our restoration needs, in most scenarios, the only sustainable source of seed is from grow-outs of wild harvested seed in agricultural settings (@pedrini2020collection, @broadhurst2015seeding,  @national2023assessment).
Enormous efforts are now underway to increase the number of species, the number of populations within these species, and the genetic diversity of these populations available for restoration @national2023assessment.
However, difficulties exist in both the wild harvest and increase of seed which are limiting our ability to develop adequate amounts of germplasm material.  
Herein, we identify prospective methods to increase the 1) number of species, 2) populations, and 3) genetic diversity of collections and 4) increase the success of agriculturally produced seed lots using Species Distribution Models and subsequent analysis of them intended to pair them more aptly with species biology and ecology.

@@

More species per restroation gooood. @wilsey2021restoration
Each collection is generally only cultivated for 1-5 generations before various effects of selection start to reduce the efficacy of the lineage in restorations (@espeland2017evolution, @pizza2021eight, @conrady2023plants)

@  "Sustainable seed harvesting in wild plant populations" different species can support different amounts of harvest. 
@ theory of how less diversity can harm restorations
